LV2

### 2018-04-24 paper.tex
Initial global analysis.

%\usepackage{times}
%\normalfont
\usepackage[T1]{fontenc}
%\usepackage[mtplusscr,mtbold]{mathtime}
%
\begin{document}
\begin{frontmatter}              % The preamble begins here.

@@

\section{GLobal analysis}
\label{sec:global-analysis}

@@

On average, about \hl{3\,000} tweets were collected per day, which is more than \hl{1\,500} by the geo-location based technique in \cite{milajevs:2017:BUCC}.

>>>>

%\usepackage{times}
%\normalfont
\usepackage[T1]{fontenc}
%\usepackage[mtplusscr,mtbold]{mathtime}
%

\newcommand{\sn}[1]{\href{https://twitter.com/#1}{\texttt{@#1}}}

\begin{document}
\begin{frontmatter}              % The preamble begins here.

@@

\section{Global analysis}
\label{sec:global-analysis}

@@

On average, about \hl{3\,200} tweets were collected per day, which is more than \hl{1\,500} by the geo-location based technique in \cite{milajevs:2017:BUCC}. Most of the tweets came from the official Twitter clients for Web, Android or iPhone. Together these clients contributed more than 60\% of all collected tweets, refer to Table~\ref{tab:source_counts} for more details.

The twitter web client is used by both: the general public and media companies. The top 5 of most active accounts consists only of tracked Latvian media accounts: \sn{DienaLV}, a newspaper, \sn{LA\_lv}, another newspaper, \sn{JaunsLV}, a media portal, \sn{TV3\_Play}, a TV channel, and \sn{dblv}, a newspaper.

Notably, for mobile clients, the majority of tweets comes from the general public, because they are either geo-located or mention a tracked account. The number of tweets coming from tracked accounts, \hl{that are mostly media}, is lower for Android \hl{(8.5\%)} than for iPhone \hl{(13.5\%)}. The difference can be explained by the fact, that all top 5 Android users are personal accounts, while for iPhone there are only 2 personal accounts in the top 5. \sn{TV3zinas}, a news account of a TV channel, tweets the most from iPhone. \sn{Lattelecom}, a telecommunication company, is the second most active iPhone user. \sn{AstrologiLv} writes about astrology and is the fourth most active iPhone user. All three accounts tweet exclusively in Latvian and were tracked during corpus collection.

Client applications that produce tweets mostly from tracked accounts are used by the media. For the TweetDeck, TVNET Login, dlvr.it and SKATIES client applications the top 5 users are tracked media accounts that write dominantly in Latvian. The exceptions are a business account \sn{Kompresori} that was not tracked and tweets in three languages: Latvian, Russian and English, \sn{RusApollo} and \sn{TVNET\_rus} who tweet identical content exclusively in Russian, and \sn{SejasLV}, an exclusively Latvian account writing about celebrities that was not tracked.

TweetDeck is used by \sn{DelfiLV}, a major media portal, \sn{LV\_Portals}, an account run by the official government gazette of the Republic of Latvia, \sn{lsmlv}, an account of a publicly funded radio and television organization (LSM), \sn{ltvzinas}, the news account of Latvian Television, \sn{RietumuRadio}, a radio station.

TVNET is a media company that controls several media portals. The most active accounts that use their application are \sn{TVnet\_portals}, \sn{RusApollo}, \sn{TVnet\_rus}, \sn{SportsTVNET}, and \sn{SejasLV}.

The tweet delivery service \texttt{dlvr.it} is used by the newspaper \sn{nralv} and their sport portal \sn{Sportacentrs}, the photo account of the national news agency (LETA) \sn{letafoto}, \sn{Kompresori} and the sport account of Latvian Television \sn{ltvsports}.

SKATIES delivers video content from several sources. The most active accounts are \sn{skatieslatvija}, \sn{lnt\_lv}, \sn{tv3lv}, \sn{BezTabuTV3} and \sn{TV3Zinas}.

Some tweets come from social media networks. Facebook content mostly comes from tracked media accounts. The top 5 most active users are: \sn{mixnews\_lv}, the Russian edition of a media portal, \sn{Otkrito}, also the Russian edition of \sn{JaunsLV}, \sn{labdienlv}, \sn{ekonimikalv} and \sn{nozare}, all three belonging to one Latvian media portal. The fact that Russian accounts are not active among other clients might suggest that Russian content is not spread via Twitter, but, for example, via Facebook.

The content that comes form Foursquare and Instagram is created by the general public.

There is a clear pattern that mobile clients are used by personal accounts, while media companies set up a special solution to deliver tweets, probably, integrating it with their content delivery systems or simply using a web client from an office machine.
